---
title: "Miscanthus: Abundance-Occupancy and Shared ASVs Report"
author:
  - "Bolívar Aponte Rolón"
date: last-modified
format:
#  html:
#    theme: cosmo
#    toc: true
#    toc-depth: 3
#    number-sections: true
#    code-fold: true
#    df-print: paged
  pdf:
    documentclass: scrartcl
    papersize: letter
    toc: true
    toc-depth: 3

execute:
  echo: true
  warning: false
  message: false
  cache: false
  freeze: auto
  # fig-width: 10
  # fig-height: 7
  fig-dpi: 150
  # fig-format: "png"
---



# About this report

This Quarto report executes two existing analysis scripts:

-   `06_alpha_beta_div.R` — Community Diversity Analyses
-   `07_abund_occupancy.R` — Abundance-Occupancy Analyses
-   `08_shared_asvs_upset_plots.R` — Shared ASVs Analyses

::: callout-note
Scripts assume project-root working directory (for sourcing `R/utils/00_setup.R`). Place this `.qmd` at the repository root so relative paths resolve as expected.

If your environment needs it, ensure all packages used by the scripts are installed before rendering.

Render from the repository root:

-   CLI: `quarto render mxg_abun_occu_report.qmd --execute-dir .`
-   R: `quarto::quarto_render("mxg_abun_occu_report.qmd")`
:::

```{r}
#| label: setup
#| include: false
# Keep objects in the global knit environment so both scripts can share state if needed
knitr::knit_hooks$set(document = function(x) x)
# sets the working directory for code execution to the repo root
knitr::opts_knit$set(root.dir = here::here())
knitr::opts_chunk$set(
  fig.width = 10,
  fig.height = 7,
  out.width = "100%",
  fig.align = "center"
)
```



# Section 1 — Abundace-Occupancy Analyses

Addresses the following questions:

1.  What are the abundance-occupancy patterns in Miscanthus microbiomes across different projects, regions, and sample types?

2.  How do these patterns vary by timing (EF), year (LAMPS 2018), and site (LAMPS 2022)?

This section runs the full workflow in [07_abund_occupancy.R](R/07_abund_occupancy.R), including:

-   Abundance-Occupancy plots

```{r}
#| label: run-abundance-occupancy
#| results: 'markup'
#| fig-cap-location: bottom
source(
  "R/07_abund_occupancy.R",
  local = knitr::knit_global(),
  echo = FALSE,
  print.eval = TRUE
)
```



# Section 2 — Alpha Diversity Analyses

This section runs [06_alpha_beta_div.R](R/06_alpha_beta_div.R), including:

-   Richness and alpha diversity summaries
-   Beta diversity ordinations

```{r}
#| label: run-diversity
#| results: 'hold'
#| fig-cap-location: bottom
source("R/06_alpha_beta_div.R", local = knitr::knit_global())
```



# Section 3 — Shared ASVs Analyses

This section runs [08_shared_asvs.R](R/08_shared_asvs.R), including: - Upset plots of shared ASVs across projects, regions, and sample types - Summary tables of shared ASVs at different prevlence thresholds

```{r}
#| label: run-shared-asvs
#| results: 'hold'
#| fig-cap-location: bottom
source(
  "R/08_shared_asvs_upset_plots.R",
  local = knitr::knit_global(),
  echo = FALSE,
  print.eval = TRUE
)
```



# Session information

```{r}
#| label: session-info
sessionInfo()
```