---
title: "Miscanthus: EDA and Community Diversity Report"
author:
  - "Bolívar Aponte Rolón"
date: last-modified
format:
#  html:
#    theme: cosmo
#    toc: true
#    toc-depth: 3
#    number-sections: true
#    code-fold: true
#    df-print: paged
  pdf:
    documentclass: scrartcl
    papersize: letter

execute:
  echo: true
  warning: false
  message: false
  cache: false
  freeze: auto
  # fig-width: 10
  # fig-height: 7
  # fig-dpi: 300
  # fig-format: "png"
---

# About this report

This Quarto report executes two existing analysis scripts:

-   `04_eda.R` — Exploratory Data Analysis of Microbial Communities
-   `05_alpha_beta_div.R` — Community Diversity Analyses

Both scripts assume project-root working directory (for sourcing `R/utils/00_setup.R`). Place this `.qmd` at the repository root so relative paths resolve as expected.

If your environment needs it, ensure all packages used by the scripts are installed before rendering.

::: callout-note
Render from the repository root:

-   CLI: `quarto render mxg_eda_report.qmd --execute-dir .`
-   R: `quarto::quarto_render("mxg_eda_report.qm")`
:::

```{r}
#| label: setup
#| include: false
# Keep objects in the global knit environment so both scripts can share state if needed
knitr::knit_hooks$set(document = function(x) x)
# sets the working directory for code execution to the repo root
knitr::opts_knit$set(root.dir = here::here())
```

# Section 1 — Exploratory Data Analysis

This section runs the full workflow in [04_eda.R](R/04_eda.R), including:

-   Dataset exploration (metadata, taxonomic distribution)
-   Read count summaries and visualizations
-   Good’s coverage estimates
-   ASV prevalence/core taxa summaries


```{r}
#| label: run-exploratory
#| results: 'markup'
#| fig-cap-location: bottom
source(
  "R/04_eda.R",
  local = knitr::knit_global(),
  echo = TRUE,
  print.eval = TRUE
)
```

# Section 2 — Alpha Diversity Analyses

This section runs [05_alpha_beta_div.R](R/04_alpha_beta_div.R), including:

-   Richness and alpha diversity summaries
-   Beta diversity ordinations


```{r}
#| label: run-diversity
#| results: 'hold'
#| fig-cap-location: bottom
source("R/05_alpha_beta_div.R", local = knitr::knit_global())
```

# Session information

```{r}
#| label: session-info
sessionInfo()
```